Clustering exploration for `r params$library_id`

### 2024-08-06 analyses/cell-type-ewings/template_notebooks/clustering-workflow/01-clustering.Rmd
some comment updates and figure size change

```{r, fig.height=15, fig.width=10}
# look at clustering results for each library across all params
ggplot(umap_df, aes(x = UMAP1, y = UMAP2, color = cluster)) +
  geom_point(alpha = 0.5, size = 0.1) +
  facet_wrap(vars(nn_param)) +
  theme(
    aspect.ratio = 1
  ) +
  guides(color = guide_legend(override.aes = list(alpha = 1, size = 1.5)))
```

@@

- Average silhouette width: This metric evaluates cluster separation. 
Cells with large positive silhouette widths are closer to other cells in the same cluster than to cells in different clusters. 
Higher values indicate tighter clusters.
- Average cluster purity: This metric also evaluates cluster separation and tells us the proportion of neighboring cells that are assigned to the same cluster. 
Higher purity values indicate that clusters are well separated. 
- Cluster stability: This evaluates how stable the clustering is to input data. 
Higher values of cluster stability indicate more reproducible clusters.

@@

```{r, fig.height=10, fig.width=5}
# plot to look at marker gene expression for all cell types across all clusters and all params
k_params <- unique(cluster_exp_df$nn_param) |>
  as.character()

>>>>

```{r, fig.height=15, fig.width=10}
# look at clustering results for each library across all params
ggplot(umap_df, aes(x = UMAP1, y = UMAP2, color = cluster)) +
  geom_point(alpha = 0.5, size = 0.1) +
  facet_wrap(vars(nn_param)) +
  theme(
    aspect.ratio = 1,
    legend.position = "none"
  )
```

@@

- Average silhouette width: This metric evaluates cluster separation. 
Cells with large positive silhouette widths are closer to other cells in the same cluster than to cells in different clusters. 
Higher values indicate tighter clusters.
- Average cluster purity: This metric also evaluates cluster separation and tells us the proportion of neighboring cells that are assigned to the same cluster. 
Purity values range from 0-1 with higher purity values indicating clusters that are well separated. 
- Cluster stability: This evaluates how stable the clustering is to input data. 
Stability values range from 01- with higher values of cluster stability indicating more reproducible clusters.

@@

```{r, fig.height=7, fig.width=7}
# plot to look at marker gene expression for all cell types across all clusters and all params
k_params <- unique(cluster_exp_df$nn_param) |>
  as.character()
